Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-24 robdml.tex
tex

\subsection{Intra-Class Structure Constraint}
\label{sec:33}

\oo{[illust fig]}

\begin{equation}
	L_\text{ICS} = \lambda \cdot L_\text{T}(
	\va, \tilde{\va}, \vp; 0)
\end{equation}

>>>>

\subsection{Intra-Class Structure}
\label{sec:33}

% motivation

During adversarial training, the adversarial counterpart of each given sample
triplet is fed to the model, and the triplet loss will enforce a good
\emph{inter-class} structure.
%
Since the anchor, positive sample, and their adversarial counterpart belongs to
the same class, it should be noted that the \emph{intra-class} structure can be
enforced as well, and This has been neglected by the existing DML defenses.
%
\emph{Intra-class} structure is also important for robustness besides the
\emph{inter-class} structure, because the attack may attempt to change the
rankings of samples in the same class~\cite{advrank}.

% Solution

We propose an additional loss function term to enforce such \emph{intra-class}
structure, as shown in \oo{Fig.~[].}
%
Specifically, the anchor $\va$ and its adversarial counterpart $\tilde{\va}$
are separated from the positve sample $\vp$ by reusing the triplet loss,
\ie,
%
\begin{equation}
	L_\text{ICS} = \lambda \cdot L_\text{T}(
	\va, \tilde{\va}, \vp; 0),
\end{equation}
%
where $\lambda$ is a constant hyper-parameter for controlling the importance
of this term.
%
$L_\text{ICS}$ can be added to the original loss function for adversarial training.
